---
title: "CS102_BSIT2C_JUNTANILLA_PRAC"
author: "JOSE ROLAND JUNTANILLA"
date: "2024-03-06"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A. Load the built-in warpbreaks dataset.
```{r}
structure(warpbreaks)
```

1. Find out, in a single command, which columns of warpbreaks are either numeric or
integer. What are the data types of each column?
```{r}
df_datatype <- sapply(warpbreaks, function(x) typeof(x))
df_datatype
#The data types of each column is double,integer,interger.
```


2. How many observations does it have?
```{r}
(obs_df <- nrow(warpbreaks))

# The dataframe warpbreaks has a 54 Observations.
```


3. Is numeric a natural data type for the columns which are stored as such? Convert to
integer when necessary.
```{r}

is.integer(warpbreaks$breaks) 

warpbreaks$wool <- as.integer(warpbreaks$wool) 
warpbreaks$tension <- as.integer(warpbreaks$tension)
warpbreaks

```

4. Error messages in R sometimes report the underlying type of an object rather than the
user-level class. Derive from the following code and error message what the
underlying type. Explain what is the error all about. Do not just copy the error
message that was displayed.
```{r}

```

B. Load the exampleFile.txt
1. Read the complete file using readLines.
```{r}
file_cont <- readLines("exampleFile.txt")
print(file_cont)
```

2. Separate the vector of lines into a vector containing comments and a vector
containing the data. Hint: use grepl.
```{r}
(com <- file_cont[grepl("//", file_cont)])


(data <- file_cont[!grepl("//", file_cont)])

```
3. Extract the date from the first comment line and display on the screen “It was created
data.”
```{r}
(date <- gsub(".*Created : ", "", com[1]))

paste0("It was created ", date)

```

4. Read the data into a matrix as follows.
a. Split the character vectors in the vector containing data lines by semicolon (;)
using strsplit.
```{r}
(splitLines <- strsplit(data, ";"))
```

b. Find the maximum number of fields retrieved by split. Append rows that are
shorter with NA's.
```{r}

(veclength <- sapply(splitLines, length))

(Fieldfmax <- max(veclength))

(splitLines <- lapply(splitLines, function(row) c(row, rep(NA, Fieldfmax - length(row)))))

```